\thesistitle

### 2019-06-14 sections/background.tex
Update conclusion from sattose paper
Just as a placeholder
Nice formula
Overall model

\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/clone-pair}
	\caption{Example of a clone pair, as found in the \href{https://github.com/taweili/ardublock}{ardublock} project.}
	\label{fig:clonepair}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/clone-class}
	\caption{Example of two clone classes.}
	\label{fig:cloneclass}
\end{figure}

\section{Clone Types}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and refactor. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

@@

>>>>

\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/clone-pair}
	\caption{Example of a clone pair, as found in the \href{https://github.com/Danny02/JOpenCTM}{JOpenCTM} project.}
	\label{fig:clonepair}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/clone-class}
	\caption{Example of a clone class, as found in the \href{https://github.com/Danny02/JOpenCTM}{JOpenCTM} project.}
	\label{fig:cloneclass}
\end{figure}

\section{Clone Types} \ref{chap:backgroundclonetypes}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and refactor. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

@@

\section{Background on refactoring methods}

### 2019-06-14 sections/research.tex
Overall structural changes
Overall model

\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
In section \ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature. These simple definitions are suitable for analysis of a codebase. Their detection results in simple to understand numbers to argue about a codebase. However, these clone types have a few flaws which makes it hard to argue to what extend two fragements of code are functionally related. For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design. Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.

@@

\section{Shortcomings of clone types}
The clone definitions, as outlined in section \ref{chap:backgroundclonetypes}, allow reasoning about the duplication in a software system. Clones by these definitions can relatively easily and efficiently be detected. This has allowed for large scale analyses of duplication. However, these clone type definitions have shortcomings which makes the clones detected in correspondance with these definitions less valuable for (automated) refactoring purposes.

@@

In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods. However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal. Both code fragments use different imported types, some of which imported via a wildcard. Because of this, it is hard to verify which of the used types have the same underlying implementation. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgement regarding the refactorability of such a clone. When aiming to automatically refactor clones, applying refactorings to clones as shown in figure \ref{fig:type1}, is bound to be error prone and result in a uncompilable project or a difference in functionality.

@@

\subsection{Type 1R clones} \label{chap:type1rclones}
We propose an alternative definition of type 1 clones. This definition requires cloned fragments to be not just textually equal, but also functionally equal. Although requiring fragements to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones). We check functional equality of two fragments by validating the equality of the fully qualityfied identifier for referenced types, methods and variables. Type 1R clones are a subset of type 1 clones.

@@

\subsubsection{Called methods}
A codebase can have several methods with the same name. The implementation of these methods might differ. When we call two methods with an identical name, we can in fact call different methods. This is another reason that textually identical code fragements can differ functionally.

@@

\section{Unifying the types}\label{sec:unifying}
In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline. In literature, these definitions are mainly aimed towards reasoning about duplication in source code. When considering these types for refactoring, the goal becomes slighly different. Because of this, having separate clone type definitions does not have any value. Rather, we need a single clone type definition by which we can detect all clones that can and should be considered for refactoring.

@@

@@

\subsection{Clone Detection}
To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure. On basis of this graph structure, clones are detection. Dependent on the type of clones being detected, transformations may be applied. The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{sec:unifying}.

@@

Building the ``clone grid'' consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
\begin{itemize}
  \item The declaration/statement preceding it.
  \item The declaration/statement following.
  \item The last \textbf{preceding} declaration/statement with which it is cloned.
\end{itemize}
We do not create a seperate grid for each class file, so the statement/declaration preceding or following could be in a different file. While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement. This map is used to quickly find out whether a statement is cloned with another. An example of such a grid is displayed in figure \ref{fig:clonegridsimple}.

@@

>>>>

\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
In section \ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature. These simple definitions are suitable for analysis of a codebase. Their detection results in simple to understand numbers to argue about a codebase. However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code are functionally related. For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design. Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.

@@

\section{Shortcomings of clone types}
The clone definitions, as outlined in section \ref{chap:backgroundclonetypes}, allow reasoning about the duplication in a software system. Clones by these definitions can relatively easily and efficiently be detected. This has allowed for large scale analyses of duplication. However, these clone type definitions have shortcomings which makes the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.

@@

In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods. However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal. Both code fragments use different imported types, some of which imported via a wildcard. Because of this, it is hard to verify which of the used types have the same underlying implementation. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone. When aiming to automatically refactor clones, applying refactorings to clones as shown in figure \ref{fig:type1}, is bound to be error prone and result in a uncompilable project or a difference in functionality.

@@

\subsection{Type 1R clones} \label{chap:type1rclones}
We propose an alternative definition of type 1 clones. This definition requires cloned fragments to be not just textually equal, but also functionally equal. Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones). We check functional equality of two fragments by validating the equality of the fully qualified identifier for referenced types, methods and variables. Type 1R clones are a subset of type 1 clones.

@@

\subsubsection{Called methods}
A codebase can have several methods with the same name. The implementation of these methods might differ. When we call two methods with an identical name, we can in fact call different methods. This is another reason that textually identical code fragments can differ functionally.

@@

\section{Unifying the types}\label{sec:unifying}
In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline. In literature, these definitions are mainly aimed towards reasoning about duplication in source code. When considering these types for refactoring, the goal becomes slightly different. Because of this, having separate clone type definitions does not have any value. Rather, we need a single clone type definition by which we can detect all clones that can and should be considered for refactoring.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{img/CloneRefactorOverall}
  \caption{CloneRefactor overall process.}
  \label{fig:clonerefactorprocess}
\end{figure}

Figure \ref{fig:clonerefactorprocess} shows the overall process used by CloneRefactor. First, we detect clones on basis of a Java codebase, given a Java project from disk and a configuration. The clone detection process is further explained in section \ref{sec:clonedetection}. After all clones are found, CloneRefactor maps the context of the clones. On basis of this context, CloneRefactor applies transformations to the source code for clones for which we have configured a refactoring.

@@

\subsection{Clone Detection}\ref{sec:clonedetection}
To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure. On basis of this graph structure, clones are detection. Dependent on the type of clones being detected, transformations may be applied. The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{sec:unifying}.

@@

Building the ``clone grid'' consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
\begin{itemize}
  \item The declaration/statement preceding it.
  \item The declaration/statement following.
  \item The last \textbf{preceding} declaration/statement with which it is cloned.
\end{itemize}
We do not create a separate grid for each class file, so the statement/declaration preceding or following could be in a different file. While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement. This map is used to quickly find out whether a statement is cloned with another. An example of such a grid is displayed in figure \ref{fig:clonegridsimple}.

@@

In this stage, \textbf{type 3R} clones have the same compare rules as type 2R clones.
